A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-30 UAM2014/Article/article.tex
la2pdf commit - 2014:04:30	13:37:52	(Wed30.Apr)

Modern GPUs are customized to perform computer graphics. Their theoretical peak performance is typically and order of magnitude higher than a CPU in a comparable price range. This performance can not always be achieved in practice, unless the algorithm can be adapted to use a well matured and optimized graphics processing API such as OpenGL. Our simulator uses OpenGL for most of the , then it makes little

Whether this performance can be achieved in practice 
Whenever conventional computer graphics processing can be used to 
GPUs are designed to provide the best possible graphics processing performance, and there large ecosystem of tools and libraries  available 
Using a GPU to drive a simulator is advantageous since

>>>>

One way to automatically classify objects in SAS images is compare the imaged objects with a predefined set of templates. These are typically simple simulations of common objects with various sizes and shapes. With luck one might be a close match, but

Template matching is a common technique for automatic classification of objects in synthetic aperture sonar (SAS) images.

We have implemented a SAS simulator that creates object templates in delayed real-time based on parameters estimated from the current scene. Compared to the conventional method  having a predefined set of object templates

, and not just a  on-the-fly based on adapted parameters, and not just a predefined set. 
Modern GPUs are customized to perform computer graphics. Their theoretical peak performance is typically and order of magnitude higher than a CPU in a comparable price range. While it is hard to obtain this performance in practice, one can get very close by using a well matured and highly optimized graphics processing API such as OpenGL. Because of this we use OpenGL for simulating a scene with 3D models of the seabed and objects.
